Supporting Information: Thermal sensitivity across forest vertical profiles: patterns, mechanisms, and ecological implications

### 2021-09-30 vertical-thermal-review.Rmd
new line for each sentence in global change section

Having established how physical conditions and biological form and function vary across vertical gradients, we now turn attention to the implications of these patterns for our understanding of how forest ecosystems may be impacted by global change, and our ability to project this across space and time.

@@

The complex interwoven relations between the biophysical environment and biological factors--leaf traits, metabolic processes and distribution of trees-- are likely to produce amplifications and feedback loops in a warming world, with implications for forests on many levels.

>>>>

Having established how physical conditions and biological form and function vary across vertical gradients (Fig. `r schematic`), we now turn attention to the implications of these patterns for our understanding of how forest ecosystems may be impacted by global change, and our ability to project this across space and time.

@@

The complex interwoven relations between the biophysical environment and biological factors -- leaf traits, metabolic processes, and distribution of species across canopy strata -- are likely to produce amplifications and feedback loops in a warming world, with implications for forests on many levels.
